### 2014-07-09 tex/main-body-text.tex
Final additions to conclusion and last paragraph.

The development of software to analyze genetic data is ever increasing. In the face of a growing
number of programs, end users must wade through a seemingly countless number of programs each with
their own assumptions, strengths, and weaknesses. Lacking a recognition of these properties
can result in the ineffectual use of both time and resources.
By providing a different prespective on the algorithm
implemented in {\sc flock} we hope to increase understanding of its applicability to a different datasets
while decreasing end user confusion and misuse.

>>>>

For many types of genetic analyses, molecular ecologists can choose from 
amongst a wide range of published methods.  Choosing one of these methods to use can
be difficult, especially when the methods have been touted as very different.
We have known colleagues whose solution to this problem is simply to run their data
through every program available.  This seems an ineffective use of time and resources 
that could be counteracted by a more transparent accounting of the similarities between
methods. As one small step toward that,   
we have provided a different prespective on the algorithm
implemented in {\sc flock}, showing it to be very similar to {\sc structure}
using a particular set of options.  We hope this might increase understanding of {\sc flock}'s applicability to different datasets while decreasing end user confusion and misuse.
